---
title: "Initial Korean covid 19"
author: "wesley cruz"
date: "spring 2023"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?






## Graphical results - use ggplot commands to do this  

```{r}
barchartGC(~result + Sex,data=kRdata)
barchartGC(~result + Sex,data=kRdata, type="percent")

```
  
Looking at the bar graph above, we can see that there are more males dying over the amount of females. The percentages for the males alive have a lower percentage compared to women.Taking a look at the frequency where the total amount of people are given, We can see that women have a higher rate of being alive when being compared to the men from this data.


  
## Numerical results


```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```

Now taking a look at the data presented above, We see the total of 36% of females dead leaving 64% of males dying. When looking at the percentages on being alive, Females are at 56% while males are left at 44%.

## Inferential results 

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

The data here now gives us the total amount of people alive and dead due to the disease.The observed count collected the data and shows that 1832 females and 1411 males are alive leaving 25 females and 44 males dead.When comparing the observed count to the expected null, We can see a difference where the expected null shows more females dying compared to men meaning the disease targets more men over females. The odds ratio for men dying would be 2.3.

## Conclusions
In conclusion, the followed up data proves that the disease located in Korea has been targeting more men over women. The first graph shows the comparison of both genders. One bar graph shows the difference between the two in being alive while the other shows the difference on deaths.The graphs show that men have a higher rate of death compared to women. The second data set shows the percent difference on both subjects of being alive and dead. Women are at a 36% rate of being dead while men are at a 64% rate of being dead. The final concluding data shows the complete amount of people who have deceased. 1831 women and 1411 men are alive. 25 women and 44 men are dead. This data shows how the disease is affected men more compared to women.
